Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-05-08 doc/thesis/discussion.tex
Highlight new things

Our use of the \gls{BA} model makes several simplifying assumptions. First, we
assume homogeneity across the network with respect to node behaviour and
transmission risk. In reality, the attraction to high-degree nodes seems likely
to vary among individuals, as does their risk of transmitting or contracting
the virus. We have also assumed that all transmission risks are symmetric,
which is clearly false for all known modes of \gls{HIV} transmission, and that
infected individuals never recover but remain infectious indefinitely. These
assumptions were made for the purpose of keeping the model as simple as
possible, since this is the very first attempt to fit a contact network model
in a phylodynamic context. However, the Gillespie simulation algorithm built
into \software{netabc} can handle arbitrary transmission and removal rates
which need not be homogeneous across the network. Moreover, it is possible to
use kernel-\gls{ABC} to fit a model which relaxes some or all of these
assumptions, which may be a fruitful avenue for future investigation. Despite
the possible misspecification, our estimates of the power law exponent $\gamma$
were within the range of values reported in the literature (\cref{tab:gamma}).

>>>>

Our use of the \gls{BA} model makes several simplifying assumptions. First, we
assume homogeneity across the network with respect to node behaviour and
transmission risk. In reality, the attraction to high-degree nodes seems likely
to vary among individuals, as does their risk of transmitting or contracting
the virus. We have also assumed that all transmission risks are symmetric,
which is clearly false for all known modes of \gls{HIV} transmission, and that
infected individuals never recover but remain infectious indefinitely. These
assumptions were made for the purpose of keeping the model as simple as
possible, since this is the very first attempt to fit a contact network model
in a phylodynamic context. However, the Gillespie simulation algorithm built
into \software{netabc} can handle arbitrary transmission and removal rates
which need not be homogeneous across the network. Moreover, it is possible to
use kernel-\gls{ABC} to fit a model which relaxes some or all of these
assumptions, which may be a fruitful avenue for future investigation. 
{\color{blue}Despite the possible misspecification, our estimates of the power
law exponent $\gamma$ were within the range of values reported in the
literature (\cref{tab:gamma}).}

### 2016-05-08 doc/thesis/preface.tex
Highlight new things

A version of chapter 2 has been submitted for publication with the title
``Reconstructing network parameters from viral phylogenies.'' An oral
presentation entitled ``Phylodynamic inference of contact network parameters
with kernel-ABC'' was given based on chapter 2 to the 23rd HIV Dynamics and
Evolution meeting on April 25, in Woods Hole, Massachusetts, USA (the
presentation was delivered remotely). A poster based on chapter 2 entitled
``Likelihood-free estimation of contact network parameters from viral
phylogenies'' was presented at the Intelligent Systems for Molecular Biology
meeting in Orlando, Florida, USA.

>>>>

A version of chapter 2 has been submitted for publication with the title
``Reconstructing network parameters from viral phylogenies.'' An oral
presentation entitled ``Phylodynamic inference of contact network parameters
with kernel-ABC'' was given based on chapter 2 to the 23rd HIV Dynamics and
Evolution meeting on April 25, 2016, in Woods Hole, Massachusetts, USA (the
presentation was delivered remotely). 
%A poster based on chapter 2 entitled
%``Likelihood-free estimation of contact network parameters from viral
%phylogenies'' was presented at the Intelligent Systems for Molecular Biology
%meeting in Orlando, Florida, USA.

### 2016-05-08 doc/thesis/results.Rnw
Highlight new things

To make our analyses comparable to the existing network literature, we
estimated values of the power law exponent $\gamma$ for each of the datasets 
investigated. The results are summarized in \cref{tab:gamma}. All of the
estimated exponents were in the range $2 \leq \gamma \leq 2.5$.

\begin{table}
    \centering
    \input{\tablepath/realdata-gamma.tex}
    \caption[
        Estimated power law exponents for six HIV datasets based on maximum
        \textit{a priori} estimates of BA model parameters.
    ]{
        Estimated power law exponents for six HIV datasets based on maximum
        \textit{a priori} estimates of BA model parameters. 100 networks were
        simulated using \textit{MAP} parameter estimates obtained with
        \software{netabc}. The power law exponent $\gamma$ was estimated for
        each, and the median of those estimates was used as a point estimate
        for the corresponding dataset.
    }
    \label{tab:gamma}
\end{table}

>>>>

{\color{blue}
To make our analyses comparable to the existing network literature, we
estimated values of the power law exponent $\gamma$ for each of the datasets 
investigated. The results are summarized in \cref{tab:gamma}. All of the
estimated exponents were in the range $2 \leq \gamma \leq 2.5$.

\begin{table}
    \centering
    \input{\tablepath/realdata-gamma.tex}
    \caption[
        Estimated power law exponents for six HIV datasets based on maximum
        \textit{a priori} estimates of BA model parameters.
    ]{
        Estimated power law exponents for six HIV datasets based on maximum
        \textit{a priori} estimates of BA model parameters. 100 networks were
        simulated using \textit{MAP} parameter estimates obtained with
        \software{netabc}. The power law exponent $\gamma$ was estimated for
        each, and the median of those estimates was used as a point estimate
        for the corresponding dataset.
    }
    \label{tab:gamma}
\end{table}
}
